---
title: "HW6_TestThat"
format: html
editor: visual
---

## Description

This document demonstrates how to use the Assignment 5 functions to create sample neighborhood data and calculate flood risk, social vulnerability, insurance retreat risk, and cumulative risk.

```{r}
## Load Functions
library(here)
source(here("Create Neighborhood Data.R"))
source(here("compute_flood_risk.R"))
source(here("calculate_vulnerability.R"))
source(here("calculate_Insurance_Retreat.R"))
source(here("cumulative_risk_function.R"))
```

# Example Neighborhood Data
```{r}
neighborhood_data <- create_neighborhood_data(n = 10)

head(neighborhood_data)
```

# Calculating the flood risk 

```{r}
neighborhood_data$flood_risk <- compute_flood_risk(
  elevation = neighborhood_data$elevation,
  distance_coast = neighborhood_data$distance_coast,
  mean_rain = neighborhood_data$mean_rain,
  num_past_floods = neighborhood_data$num_past_floods
)

head(neighborhood_data)
```

# Calculating the Social Vulnerability


```{r}
neighborhood_data$vulnerability_score <- calculate_vulnerability(
  low_inc = neighborhood_data$low_inc,
  minority = neighborhood_data$minority,
  no_insurance = neighborhood_data$no_insurance,
  renters = neighborhood_data$renters,
  elderly = neighborhood_data$elderly,
  children = neighborhood_data$children,
  disabled = neighborhood_data$disabled
)

head(neighborhood_data)
```

# Calculating Insurance Retreat Score

```{r}
neighborhood_data <- calculate_insurance_retreat_score(neighborhood_data)

head(neighborhood_data)
```

# Calculate Cumulative Risk

```{r}
neighborhood_data$cumulative_risk_index <- compute_risk_index(
  flood_vulnerability = neighborhood_data$flood_risk,
  social_vulnerability = neighborhood_data$vulnerability_score,
  non_coverage_risk = neighborhood_data$insurance_retreat_score
)

head(neighborhood_data)
```

# The Final Output

```{r}
final_output <- neighborhood_data[
  c("city", "flood_risk", "vulnerability_score",
    "insurance_retreat_score", "cumulative_risk_index")
]

final_output
```

# Explanation
This example shows how all five of the Assignment 5 modules can be used together to assess flood/social vulnerability at the neighborhood level. First, sample neighborhood data is generated using create_neighborhood_data(). Then, flood risk, social vulnerability, and insurance retreat score are calculated separately, but require inputs from the following modules to run accordingly. Finally, each metric is combined into a cumulative risk index through the compute_risk_index() function. This provides a measure if the overall neighborhood risk!


